### 2013-09-23 structured_prediction/paper.tex
more crf blabla

>>>>

\section{CRFs for Semantic Segmentation}
Structured models based on factor graphs, as described in \Secref{factor_graphs} are often
referred to as Conditional Random Fields (CRFs), pointing to their
probabilistic interpretation.
Conditional Random Fields have been established as an important tool in many
areas of computer vision. Applications include dense stereo, optical flow, 
inpainting, de-noising, image editing, low-level segmentation and semantic segmentation.

Most conditional random fields only apply unary and pairwise potential functions. In this case, FIXME equation 4.4
becomes
\begin{equation}\eqlabel{energy_crf}
    g(x, y) = \sum_{v \in V} \psi_v(x, y_v) + \sum_{(v, w) \in E} \psi_{v,w}(x, y_{v}, y_{w}).
\end{equation}
Here $V$ enumerates variables, and $E\subset V \times V$ is a set of edges,
representing pairwise factors.

There are broadly two types of models that are used: models in which each pixel
in an image is represented as a variable, and models in which pixels are first
grouped together into superpixels and each superpixel is represented as a variable.
In pixel-based CRFs edges are usually introduced between adjacent pixels, that is using
either 4-neighborhoods or 8-neighborhoods. Superpixel-based approaches introduce
edges between adjacent superpixels, that is those that share a boundary.
%TODO images of superpixels!
%TODO looooppsss!!!!

The motivation for using superpixels is that it is often easy to group nearby
pixels that belong to the same object just based on local color or texture cues.
While it is hard to even define what makes a sensible segmentation of an image,
it is much easier to define, and also to compute an \emph{over-segmentation}.
The only requirement for an over-segmentation is that each segment only
contains pixels belonging to the same entity.

Using superpixels instead of pixels has large computational advantages.  A
model that uses superpixels contains much fewer variables than one that works
on pixel-level.  Typical sizes for superpixels are in the hundereds of pixels,
leading to a hundred-fold decrease in the number of variables. There are also
semantic advantages. Using superpixels can constitute a form of regularization,
including prior knowledge about the structure of images. Modeling interactions
between superpixels also allows more distant parts of an image to interact,
instead of modeling long-term relations only indirectly over neighbors.
Finally, modeling decisions on a superpixel-level allows for more context for a
local decision, while semantic decisions on pixel-level are not meaningful near
object boundaries.  The main disadvantage of superpixel-based approaches is
that the initial oversegmentation can not be influenced by later reasoning.
This can be a problem if fine structures need to be segmented for which local
evidence does not suffice.

% about algorithms, slic?
% hierarchical\dots has superpixels and pixels?

% submodular/non-submodular? higher order?

Conditional random fields were first used in the context of semantic
segmentation by \citet{he2004multiscale}.  Who used contrastive divergence for
learning parameters. Many other early models, such as the one of
\citet{shotton2006textonboost}, did not learn parameters at all, but used
\emph{contrast-sensitive Potts potential}. These potentials have a smoothing
effect over labels by encouraging neighboring variables to take the same value.
The penalty for taking different values is dependent on color contrast between
the pixels.

This smoothing approach was improved upon by \citet{kohli2009robust}, who
introduces higher order potentials to enforce label consistency within larger
regions. Later, \citet{ladicky2009associative} proposed a hierarchical model,
including the higher order potentials of \citet{kohli2009robust}, and
additional lateral and hierarchical connections. A similar approach, using
superpixels as the finest resolution, and additionally modelling object class
coocurrences was suggested by \citet{gonfaus2010harmony}.  However, all these
models did not learn the potentials of the CRF model in a principled manner.
The above approaches all learned unary potentials using a non-structured
approach, for example SVMs or boosting, and then set pairwise and higher order
potentials in the model by hand.

\citet{szummer2008learning} on the other hand used a structured support vector
machine approach to learn unary and pairwise parameters. They use the classical
graph cut approach of \citet{boykov2001fast} for inference.  However, graph-cut
inference is only applicable to submular energies, and therefore severly
restricts the expressivity of the resulting model.

\citet{lucchi2011spatial} investigated the importance of global constraints,
using an approach similar to \citet{szummer2008learning}, but also learning
global interactions---however, these did not improve performance, compared to
simply including global descriptors into local classifiers.

The problem of approximate inference was addressed elegantly by
\citet{yao2012describing}, who learn a joint model for scene classification,
object localization and semantic segmentation.  Their work is based on
\citet{hazan2010primal}, who integrate learning and inference in a joint
optimization problem.

%TODO where does that leave us now?
In Chapter~\ref{exact_learning} and Chapter~\ref{nyu}, we investigate
superpixel-based conditional random fields learned with conditional random
fields. Our emphasis is on understanding the learning, and how to cope with the
complexity of inference in loopy models.
